{\fontfamily{ptm}\selectfont Lorum ipsum}

### 2025-07-02 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

        \begin{definition}[SNAPG-V1 \textcolor{red}{DOESN'T WORK WELL}]\;\label{def:snapg-v1}\\
            Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
            Let $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$. 
            Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
            The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
            \begin{align*}
                & (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu^{(I_k)}/L_k\right), \\
                & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
                & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
                & x_k =  T_{L_k}(y_k | F_{I_k}) \text{ s.t: } D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
            \end{align*}
        \end{definition}
        \begin{remark}
            The sequence $\alpha_k$ is a random variable because it changes according to variable $I_k$ at the current iteration.
            This decision is made because if Theorem \ref{thm:pg-ineq} needs to hold during each iteration of the algorithm.
        \end{remark}

        \begin{theorem}[SNAPG one step inequality \textcolor{red}{INVALIDATED}]
            Let sequences of iterates $(y_k, x_k, v_k)_{k \ge 0}$ satisfy SNAPG (Definition \ref{def:snapg-v1}). 
            Denote $\mathbb E_k [\cdot]$ to be the conditional expectation on $I_{0}, I_1, \ldots, I_{k - 1}$. 
            Then, for all $k \ge 1$ the following inequality is true: 
            $$
            \begin{aligned}
            & - F(\bar x) + 
            \mathbb E_k \left[
                F_{I_k}(x_k)
            \right]
            + \mathbb E_k
            \left[
                \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
            \right]
            &\le (1 - \mathbb E_k [\alpha_k])
                \mathbb E \left[F(x_{k - 1})\right]
                F(\bar x)
                \mathbb E_k 
                \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2\right]
            \end{aligned}
            $$
            For one step, a specific function $F_{I_k}$ is sampled. 
            $F_{I_k}$ is $K^{(I_k)} > \mu^{(I_k)} \ge 0$ strongly convex and smooth. 
            The iterates $x_k, v_k$ is a function of random variable $I_k$, conditioned on all $I_{k - 1}, I_{k - 2}, \ldots , I_0$
            The sequence $\alpha_k$ is a sequence of random variable and, the relations between $\alpha_k, \alpha_{k - 1}$ is given by: 
                \alpha_k &= 
                    -\frac{L_{k - 1}\alpha_{k - 1}^2}{L_k} + \frac{\mu^{(I_k)}}{L_k} 
                    + \sqrt{
                            \frac{\mu^{(I_k)}}{L_k}
                            - \frac{\alpha_{k - 1}^2L_{k - 1}}{L_k}
                        \right)^2
                        + \frac{\alpha_{k - 1}4L_{k - 1}}{L_k}
            The relationship $(L_{k - 1}/L_k)(1 - \alpha_k)\alpha_{k - 1}^2 = \alpha_k(\alpha_k - \mu^{(I_k)}/L_k)$ is an instance of Definition \ref{def:rwapg-seq} where $\rho_{k - 1} = L_{k - 1}/L_k$. 
            Therefore, the one-step convergence result of \ref{thm:onestep-napg-cnvg} applies to function $F_{I_k}$ with sequence $\alpha_k$ and, it yields: 
                & - F_{I_k}(\bar x) + F_{I_k}(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
                & \le 
                    F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
            We take the conditional expectation on the LHS and, it has 
                & \mathbb E_k 
                \left[
                    - F_{I_k}(\bar x) + F_{I_k}(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \right]
                \mathbb E_k \left[- F_{I_k}(\bar x)\right]
                \mathbb E_k \left[F_{I_k}(x_k)\right]
                \mathbb E_k \left[
                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \right]
                &\underset{\text{(a)}}{=} 
                - F(\bar x) + 
                \mathbb E_k \left[
                    F_{I_k}(x_k)
                \right]
                + \mathbb E_k
                \left[
                    \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \right]. 
            At label (a), we make use of interpolation hypothesis which makes $\mathbb E_k[F_{I_k}(\bar x)] = F(\bar x)$. 
            Next, taking the conditional expectation on the RHS it has 
                & \mathbb E_k\left[
                    (1 - \alpha_k)
                    F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
                \right]
                &\underset{\text{(b)}}{=}
                \mathbb E_k\left[1 - \alpha_k\right]
                \mathbb E_k
                    \left[
                        F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) 
                    \right]
                &\neq 
                \mathbb E_k
                \left[1 - \alpha_k\right]
                \mathbb E_k \left[F_{I_k}(x_{k - 1})\right] - F(\bar x)
                    \mathbb E_k \left[\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2\right]
            At (b), we need to make use of covariance between the two random variable... 
            Consider random variables $X_k = (1 - \alpha_k)$ and $Y_k = F_{I_k}(x_{k - 1}) - F_{I_k}(\bar x) + \alpha_{k - 1}L_{k - 1}/2\Vert \bar x - v_{k - 1}\Vert^2$ which are functions of $I_k$ conditioned on $\alpha_{k - 1}$ and, $x_{k - 1}, v_{k - 1}$. 
            The conditional expectation of their product has $\mathbb E_k[X_kY_k] = \mathbb E_k[X_k] \mathbb E_k[Y_k] + \cov[X_k, Y_k]$.
            \textcolor{red}{Hence, taking the expectation doesn't follow. }

@@

        \begin{theorem}[SNAPG-V2 one step convergence]

@@

@@

                \item[(b)] We can use Jesen's inequality of Theorem \ref{thm:jesen} with $z = z_k$ on $F_i$. 

@@

@@

@@

            From Definiton \ref{def:snapg-v2}, it has

@@

            The proof is direct algebra and it has: 

@@

@@

                \right)^2}{L_k - \mu^{(i)}} 

@@

                \right)^2}{L_k - \mu^{(i)}} 
                - \frac{\alpha_k(L_k\alpha_k - \mu^{(i)})}{2}

@@

>>>>

@@

        \begin{lemma}[range of the momentum sequence in SNAPG-V2]

        \end{lemma}

        \begin{theorem}[SNAPG-V2 one step convergence]\label{thm:snapg2-one-step}

@@

            With following intermediate results the proof can be built easily. 
            Results (d)-(g) is showed at the end. 

@@

                \item[(b)] We can use Jensen's inequality of Theorem \ref{thm:jesen} with $z = z_k$ on $F_i$. 

@@

                \item[(d)] From Definition \ref{def:snapg-v2} it has the following equality 
                    z_k - y_k 
                    = 
                    \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
                \item [(e)] From Definition \ref{def:snapg-v2} it has: $(\forall k \ge 1)\; z_k - x_k = \alpha_k (\bar x - v_k)$. 
                \item [(f)] Using direct algebra, we have for all $k \ge 1$: 
                    \frac{\left(\mu^{(i)}\right)^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} 
                    = \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
                \item [(g)] Using (c), we have for all $k \ge 1$: 
                    \right)^2}{2(L_k - \mu^{(i)})} 
                    = 
                    \frac{
                        \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
                        \left(\alpha_k - 1\right)
                    {2(L_k - \mu^{(i)})}
                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2}. 

@@

            Starting with (a) we have: 
            \begin{align}\label{ineq:snapg2-one-step-chain1}
                \begin{split}
                    0 &\le F_i(z_k) - F_i(x_k) - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2
                    \alpha_k F_i(\bar x) + (1 - \alpha_k)F_i(x_{k - 1}) - F_i(x_k) \\
                        - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
                        + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2. 
                \end{split}
            \end{align}
            And we have the following chain of equalities:
            {\allowdisplaybreaks
                & - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
                + \frac{L_k - \mu^{(i)}}{2}\Vert z_k - y_k\Vert^2
                - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2 
                    \\&\quad
                    + \frac{L_k - \mu^{(i)}}{2}
                        \frac{L_k\alpha_k - \mu^{(i)}}{L_k - \mu^{(i)}}(\bar x - v_{k - 1})
                        + \frac{\mu^{(i)}(1 - \alpha_k)}{L_k - \mu^{(i)}}(\bar x - x_{k - 1})
                - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2 
                    \\&\quad
                    + \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} \Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{(\mu^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})}\Vert \bar x - x_{k - 1}\Vert^2 
                    \\&\quad 
                    + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
                    \frac{(\mu^{(i)})^2(1 - \alpha_k)^2}{2(L_k - \mu^{(i)})} - \frac{\mu^{(i)}\alpha_k(1 - \alpha_k)}{2}
                        \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
                    \right) \Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
                    \\&\quad 
                    + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
                \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
                {2\left(L_k - \mu^{(i)}\right)} \Vert \bar x - x_{k - 1}\Vert^2
                        \frac{(L_k\alpha_k - \mu^{(i)})^2}{2(L_k - \mu^{(i)})} - \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2}
                    \right) \Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
                    \\&\quad 
                    + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
                & \underset{\text{(g)}}{=} 
                \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}
                {2\left(L_k - \mu^{(i)}\right)}\Vert \bar x - x_{k - 1}\Vert^2
                        \frac{
                            \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
                            \left(\alpha_k - 1\right)
                        {2(L_k - \mu^{(i)})}
                        + \frac{\alpha_k(\mu - \mu^{(i)})}{2}
                    \right) \Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{(L_k\alpha_k  - \mu^{(i)})\mu^{(i)}(1 - \alpha_k)}{(L_k - \mu^{(i)})}\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
                \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}\left(
                    \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle \bar x - v_{k - 1}, \bar x - x_{k - 1}\rangle
                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2
                &= \frac{(\alpha_k - 1)\mu^{(i)}\left(L_k\alpha_k - \mu^{(i)}\right)}{2\left(L_k - \mu^{(i)}\right)}
                    \Vert x_{k - 1} - v_{k - 1} \Vert^2
                    + \frac{\alpha_k(\mu - \mu^{(i)})}{2} \Vert \bar x - v_{k - 1}\Vert^2
                    + \frac{\alpha_{k - 1}^2L_{k - 1}(1 - \alpha_k)}{2} \Vert \bar x - v_{k - 1}\Vert^2.
            Substituting the above back to the tail of Inequality \eqref{ineq:snapg2-one-step-chain1} it gives:

@@

            \textbf{Proof of (d)}.
            From Definition \ref{def:snapg-v2}, it has

@@

            The proof is direct algebra and, it has: 

@@

            \textbf{Proof of (g)}.

@@

                \right)^2}{2(L_k - \mu^{(i)})} 

@@

                \right)^2}{2(L_k - \mu^{(i)})} 
                - \frac{\alpha_k\left(L_k\alpha_k - \mu^{(i)}\right)}{2}

@@

                \frac{L_k \alpha_k - \mu^{(i)}}{2(L_k - \mu^{(i)})}\left(
                    L_k \alpha_k - \mu^{(i)} 
                    - \left(L_k - \mu^{(i)}\right)\alpha_k
                + \frac{\alpha_k(\mu - \mu^{(i)})}{2}
                &= \frac{L_k \alpha_k - \mu^{(i)}}{2(L_k - \mu^{(i)})}\left(
                    \mu^{(i)}\alpha_k - \mu^{(i)} 
                + \frac{\alpha_k(\mu - \mu^{(i)})}{2}
                \frac{
                    \left(L_k \alpha_k - \mu^{(i)}\right)\mu^{(i)}
                    \left(\alpha_k - 1\right)
                {2(L_k - \mu^{(i)})}
                + \frac{\alpha_k(\mu - \mu^{(i)})}{2}. 
